### 2017-12-24 article.tex
revising section 8

\subsection{Dividend Policy Performed by JD.com}
JD.com, Inc. does not reflect an active attitudes towards dividend payment. So far the Group have not declared or paid any dividends on ordinary shares, nor it have any present plan to pay any cash dividends on ordinary shares in the foreseeable future\footnote{See JD.com, Inc. annual report 2016, Page 131}. In the light of its heavy financial losses, it is not surprising that the Group Chose not to grant any dividends. The reason why stockholders are willing to purchase and hold the Group's stocks is unlikely for possible dividends. Instead, they may value its dominant position in electronic commerce and look ahead its future development with an optimistic expectation.

@@

JD.com, Inc. holds outstanding shares consisting of ordinary shares, series A and A-1 convertible preferred shares and series B convertible preferred shares\footnote{See JD.com, Inc. annual report 2016, Page F-10}.

\begin{table}[H]	
	\begin{center}
		\begin{tabular}{lrr}
			\toprule
			&\textbf{2015}&\textbf{2016}\\
			\midrule
			Cash and cash equivalents&17,863,868&19,771,695\\
			Restricted cash&2,114,913&4,391,955\\
			Short-term investments&2,780,482&4,391,955\\
			Investment securities&-&723,449\\
			Accounts receivable, net&8,193,665&17,464,408\\
			Advance to suppliers&927,177&1,423,736\\
			Inventories, net&20,539,543&28,909,438\\
			Loan receivables, net&3,698,488&12,697,915\\
			Other investments&-&10,766,920\\
			Prepayments and other current assets&1,486,441&2,198,906\\
			Amount due from related parties&\underline{863,516}&\underline{1,410,050}\\
			\qquad\emph{Total current assets}&\uuline{58,468,093}&\uuline{106,932,098}\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Current assets (in thousands of RMB \textyen)}\label{table:1}
\end{table}

@@

\begin{table}[H]	
\begin{center}
	\begin{tabular}{lrr}
		\toprule
		&\textbf{2015}&\textbf{2016}\\
		\midrule
		Cash and cash equivalents&17,863,868&19,771,695\\
		Restricted cash&2,114,913&4,391,955\\
		Short-term investments&2,780,482&4,391,955\\
		Investment securities&-&723,449\\
		Accounts receivable, net&8,193,665&17,464,408\\
		Advance to suppliers&927,177&1,423,736\\
		Inventories, net&20,539,543&28,909,438\\
		Loan receivables, net&3,698,488&12,697,915\\
		Other investments&-&10,766,920\\
		Prepayments and other current assets&1,486,441&2,198,906\\
		Amount due from related parties&\underline{863,516}&\underline{1,410,050}\\
		\qquad\emph{Total current assets}&\uuline{58,468,093}&\uuline{106,932,098}\\
		\bottomrule
	\end{tabular}
\end{center}
	\caption{Current assets (in thousands of RMB \textyen)}\label{table:1}
\end{table}
As we can see, the current assets jumped from \textyen58,468,093,000 to \textyen106,932,098,000.

@@

It indicates that the current liabilities jumped from \textyen104,726,000 to \textyen104,740,235,000.

\subsection{Working Capital}
\begin{table}[H]	
	\begin{center}
		\begin{tabular}{lrr}
			\toprule
			&\textbf{2015}&\textbf{2016}\\
			\midrule
			Working capital&9,485,092&2,191,863\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Working capital (In thousands of RMB \textyen)}\label{table:1}
\end{table}

\subsection{Current Ratio}
\begin{table}[H]	
	\begin{center}
		\begin{tabular}{lrr}
			\toprule
			&\textbf{2015}&\textbf{2016}\\
			\midrule
			Current ratio&1.194&1.021\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Current ratio}\label{table:1}
\end{table}

\subsection{Quick Ratio}
\begin{table}[H]	
	\begin{center}
		\begin{tabular}{lrr}
			\toprule
			&\textbf{2015}&\textbf{2016}\\
			\midrule
			Quick ratio&29,819,341&4,391,955\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Quick ratio}\label{table:1}
\end{table}

>>>>

\subsection{Dividend Policy Performed by the Group}
JD.com, Inc. does not reflect an active attitudes towards dividend payment. So far the Group have not declared or paid any dividends on ordinary shares, nor it have any present plan to pay any cash dividends on ordinary shares in the foreseeable future\footnote{See JD.com, Inc. annual report 2016, Page 131}. In the light of its heavy financial losses, it is not surprising that the Group Chose not to grant any dividends. The reason why stockholders are willing to purchase and hold the Group's stocks is unlikely for possible dividends. Instead, they may value its dominant position in electronic commerce and look ahead its future development with an optimistic expectation.

@@

\subsection{Share capital}

JD.com, Inc. holds outstanding shares consisting of ordinary shares, series A and A-1 convertible preferred shares and series B convertible preferred sharesas of December 31, 2013\footnote{See JD.com, Inc. annual report 2016, Page F-10}. Since 2014, the Group only has one class of shares, which is the Ordinary shares.

\begin{table}[H]	
	\begin{center}
		\begin{tabular}{|p{5.6cm}|r|r|r|r|}\hline
			&\multicolumn{2}{c|}{\textbf{Ordinary shares}}&\multicolumn{2}{c|}{\textbf{Treasury stock}}\\
			\hline
			&\multicolumn{1}{c|}{Shares}&Amount&\multicolumn{1}{c|}{Shares}&Amount\\
			\hline
		\rowcolor[gray]{.95}	
		Balance as of
		December 31,
		2015&2,793,756,650&358&(51,766,164)&(3)\\
		Issuance of ordinary shares&144,952,250&19&-&-\\
		\rowcolor[gray]{.95}
		Surrender of ordinary shares by certain	shareholder&(1)&-&-&-\\
		Exercise of sharebased	awards&-&-&2,820,648&77,496\\
		\rowcolor[gray]{.95}
		Share-based	compensation and vesting of sharebased	awards&-&-&8,812,582&78,903\\
		Balance as of December 31, 2016&2,938,708,899&377&(102,264,502)&(5,181,880)\\
			\hline
		\end{tabular}
	\end{center}
	\caption{Share capital (amounts in thousands of RMB \textyen, shares in one)}\label{table:1}
\end{table}

\subsection{Bonus Issue}
A bonus issue, also known as a scrip issue or a capitalization issue, is an offer of free additional shares to existing shareholders. A company may decide to distribute further shares as an alternative to increasing the dividend payout. For example, a company may give one bonus share for every five shares held.

Companies give away bonus shares to shareholders when companies are short of cash and shareholders expect a regular income. Shareholders may sell the bonus shares and meet their liquidity needs. Bonus shares may also be issued to restructure company reserves. Issuing bonus shares does not involve cash flow. It increases the company’s share capital but not its net assets.

\subsection{Stock Split}
A stock split is a corporate action in which a company divides its existing shares into multiple shares to boost the liquidity of the shares. Although the number of shares outstanding increases by a specific multiple, the total dollar value of the shares remains the same compared to pre-split amounts, because the split does not add any real value. The most common split ratios are 2-for-1 or 3-for-1, which means that the stockholder will have two or three shares, respectively, for every share held earlier.

A stock split is also known as a forward stock split. In the UK, a stock split is referred to as a scrip issue, bonus issue, capitalization issue, or free issue.

\subsection{Rights Issue}
A rights issue is a dividend of subscription rights to buy additional securities in a company made to the company's existing security holders. When the rights are for equity securities, such as shares, in a public company, it is a non-dilutive pro rata way to raise capital. Rights issues are typically sold via a prospectus or prospectus supplement. With the issued rights, existing security-holders have the privilege to buy a specified number of new securities from the issuer at a specified price within a subscription period. In a public company, a rights issue is a form of public offering (different from most other types of public offering, where shares are issued to the general public).

Rights issues may be particularly useful for all publicly traded companies as opposed to other more dilutive financing options. As equity issues are generally preferable to debt issues from the company's viewpoint, companies usually opt for a rights issue in order to minimize dilution and maximize the useful life of tax loss carry forwards. Since in a rights offering there is no change of control and a "no-sale theory" applies, companies are able to preserve tax loss carry-forwards better than via either follow-on offerings or other more dilutive financings. It's one of the types in modes of issue of securities both in public and private companies.

@@

\begin{table}[H]	
\begin{center}
	\begin{tabular}{lrr}
		\toprule
		&\textbf{2015}&\textbf{2016}\\
		\midrule
		Cash and cash equivalents&17,863,868&19,771,695\\
		Restricted cash&2,114,913&4,391,955\\
		Short-term investments&2,780,482&4,391,955\\
		Investment securities&-&723,449\\
		Accounts receivable, net&8,193,665&17,464,408\\
		Advance to suppliers&927,177&1,423,736\\
		Inventories, net&20,539,543&28,909,438\\
		Loan receivables, net&3,698,488&12,697,915\\
		Other investments&-&10,766,920\\
		Prepayments and other current assets&1,486,441&2,198,906\\
		Amount due from related parties&\underline{863,516}&\underline{1,410,050}\\
		\qquad\emph{Total current assets}&\uuline{58,468,093}&\uuline{106,932,098}\\
		\bottomrule
	\end{tabular}
\end{center}
	\caption{Current assets (in thousands of RMB \textyen)}\label{table:1}
\end{table}
As we can see, the current assets jumped from \textyen58,468,093,000 to \textyen106,932,098,000. The total current assets increased substantially by 82.89\% in fiscal year 2016 as compared to fiscal year 2015. The item other investments accounts for a great portion of the increase. The Group invests in marketable equity securities to meet business objectives. These marketable securities are reported at fair value, classified and
accounted for as available-for-sale securities in investment securities.

Other investments represent the higher yield investments purchased by JD Finance and resold to third-party investors. JD Finance will earn yield
differentials. As JD Finance takes the majority risks and rewards of the products sold to the third-party investors, the Group reported the investments
purchased and the funds raised by sale of the financial products on a gross basis on the Consolidated Balance Sheets.

In December 2014, the Group acquired 6.5\% equity interest in Tuniu with cash consideration of RMB305,930 (“Initial Investment”). Tuniu is a leading
online leisure travel company in China that is listed on the Nasdaq. The Group accounted for the Initial Investment as an available-for-sale security\footnote{F 41}.

@@

It indicates that the current liabilities jumped from \textyen48,983,001,000 to \textyen104,740,235,000. Current liabilities increased by 113.83\%. It is mainly because of a a sharp rise in Advance from customers.

\subsection{Working Capital}
The working capital of the Group is tabulated as follows:
\begin{table}[H]	
	\begin{center}
		\begin{tabular}{lrrr}
			\toprule
			&\textbf{2015}&\textbf{2016}&\textbf{Change}\\
			\midrule
			Working capital&9,485,092&2,191,863&(76.89\%)\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Working capital (In thousands of RMB \textyen)}\label{table:1}
\end{table}

Working capital is a measure of a company’s efficiency and short-term financial health. The 76.89\% decrease in working capital in fiscal year 2016 signifies underling problem on healthier liquidity.

\subsection{Current Ratio}
The Current ratio of the Group is tabulated as follows:
\begin{table}[H]	
	\begin{center}
		\begin{tabular}{lrrr}
			\toprule
			&\textbf{2015}&\textbf{2016}&\textbf{Change}\\
			\midrule
			Current ratio&1.194&1.021&14.49\%\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Current ratio}\label{table:1}
\end{table}

The current ratio measures an entity’s ability to repay its short-term obligations. .
The decreasing current ratio also implies that the Group are under pressure to pay the creditor back. Some potential creditors may doubt whether the Group in question would be able to pay off its obligations if they came due at that point.

\subsection{Quick Ratio}
\begin{table}[H]	
	\begin{center}
		\begin{tabular}{lrr}
			\toprule
			&\textbf{2015}&\textbf{2016}\\
			\midrule
			Quick ratio&29,819,341&4,391,955\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Quick ratio}\label{table:1}
\end{table}
The quick ratio reflects the ability of a company to repay its short-term obligations with its more liquid assets. It is a more stringent measure as compared to the current ratio. The 13.4\% increase in FY 2007 indicates a better capability of the Group in meeting its current liabilities with its available liquid assets. This increase was effected mainly due to the large increase in cash and cash equivalents coupled with the drop in current liabilities.
